%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[conference]{IEEEtran}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amsfonts}
\usepackage[backend=biber,bibencoding=utf8,style=ieee]{biblatex}
\usepackage{comment}
\usepackage[T1]{fontenc}
\usepackage[acronym,shortcuts,nowarn]{glossaries}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[switch]{lineno}
\usepackage{xcolor}
\usepackage{xspace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% paper specific commands
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\email}[1]{\href{mailto:#1}{\texttt{#1}}}

\newcommand{\Dissent}{Dissent\xspace}
\newcommand{\Tor}{Tor\xspace}
\newcommand{\Verdict}{Verdict\xspace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% paper specific settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\makeglossaries
\InputIfFileExists{abbrev/acronyms}{}{}
\bibliography{bib/db.bib}
\hypersetup{
	colorlinks=false,
	pdfborder={0 0 0},
}
\renewcommand\thelinenumber{\color{gray}\arabic{linenumber}}
\linenumbers % [LINE NUMBERS ARE REQUIRED BECAUSE OF THE REVIEW] comment this line if you don't want linenumbers 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% paper specific information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{State of the Art in Dining Cryptographer Networks}
\author{%
	\IEEEauthorblockN{
		Jakob Gruber
	}
	\IEEEauthorblockA{\itshape%
		Vienna University of Technology\\
		Industrial Software (INSO)\\
		1040 Vienna, Austria\\
		E-mail: \email{jakob.gruber@gmail.com}
	}
}
\IEEEspecialpapernotice{Student Paper for \emph{183.606 Seminar aus Security SE}, WS2013}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

\begin{abstract}
    \acp{DCNetwork} are anonymity networks which provide provably strong anonymity
    as well as immunity to traffic analysis attacks. On the other hand, the original
    \ac{DCProtocol} has difficulties detecting and ejecting internal disruptors.
    Likewise, scalability is limited since $O(n^3)$ messages are sent in each
    round.
    
    Since their inception, a number of new contributions have been made addressing
    these and other concerns. k-anonymous messaging improves scalability through
    relaxed security guarantees. \Dissent introduces the use of an anonymous shuffle protocol
    for transmission slot reservations and accountability through a retroactive blame
    protocol. \Verdict improves on this further with a proactively accountable
    \ac{DCNetwork} primitive which allows for efficient recovery from disruption.
    
    In this paper, we present a brief introduction to the base \ac{DCProtocol},
    k-anonymous messaging, \Dissent and \Verdict.
\end{abstract}

\begin{IEEEkeywords}
	dining cryptographers, anonymity, mix network, non-interactive, privacy.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{chapters.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\printbibliography

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
\endinput
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
